An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-10-09 paper.tex
Renaming one of the sections.
Opening paragraphs of the introduction.

\author{Karol Langner\\
        \and
        Marc Harper\\
        \and
        Owen Campbell\\
        \and
        Vincent Knight\\
}

@@

@@

\section{New strategies and implications}\label{sec:new-strategies-and-implications}

>>>>

\author{Owen Campbell\\
        \and
        Marc Harper\\
        \and
        Vincent Knight\\
        \and
        Karol Langner\\
}

@@

In 1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which
described a computer tournament that has been at the origin of a majority of
game theoretic work~\cite{readallthepapers}.

The tournament is based on an iterated game (see~\cite{Maschler2013} or similar
for details) where two players repeatedly play the normal form game of
(\ref{equ:one-shot}) in full knowledge of each others playing history to date:

\begin{equation}
    \begin{pmatrix}
        3,3 & 0,5\\
        5,0 & 1,1
    \end{pmatrix}
    \label{equ:one-shot}
\end{equation}

The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. This is a game with the following rhetoric:

\begin{quote}
    Two players have committed some sort of crime and have been separated for
    questioning, if they \textit{Cooperate} which each other and do not confess
    they will receive a reduced sentence (corresponding to the advantageous utility
    of \(3\) in (\ref{equ:one-shot})). If however, one of them cooperate and the
    other \textit{Defects} then the cooperator will receive a heavier sentence
    (corresponding to a utility of \(0\)) and the defector will be offered a deal
    (corresponding to a utility of \(5\)). If both players defect they both receive
    longer sentences (corresponding to a utility of \(1\)).
\end{quote}

Axelrod's tournaments (and further implementations of these) are sometimes
referred to as Iterated Prisoner's Dilemma tournaments.

@@

\section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}
